---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Installation

You can install `tbltools` from github with the devtools package. If you do not already have many of the dependencies installed (dplyr, stringr, ghql, httr, readxl, knitr, rmarkdown), this may take a moment to install.

```{r gh-installation, eval = FALSE}
install.packages("devtools") # skip this if you have devtools already installed
devtools::install_github("KopfLab/tbltools")
```

## Functionality

### iRAT/tRAT generation

The `tbltools` package provides functionality to easily generate Readiness Assessment Tests from a collection of questions and answers and any IF-AT answer key. For an example of how to use this functionality, see the [`demo_RAT`](demo_RAT) folder.

### Peer Evaluations

in progress

### GitHub Classroom integration

not documented yet

