---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
version <- as.character(packageVersion("tbltools"))
```

# tbltools

[![Git_Hub_Version](https://img.shields.io/badge/GitHub-`r version`-orange.svg?style=flat-square)](/commits)
[![Last-Update](https://img.shields.io/badge/updated-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits)
[![Documentation](https://img.shields.io/badge/docs-online-green.svg)](https://kopflab.github.io/tbltools/reference/)
[![Build Status](https://travis-ci.org/KopfLab/tbltools.svg?branch=master)](https://travis-ci.org/KopfLab/tbltools)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/KopfLab/tbltools?branch=master&svg=true)](https://ci.appveyor.com/project/KopfLab/tbltools)

## About

The [tbltools](https://kopflab.github.io/tbltools/) package is a collection of tools for team-based-learning (TBL) style flipped classrooms. 

## Installation

You can install [tbltools](https://kopflab.github.io/tbltools/) from github with the devtools package. If you do not already have many of the dependencies installed, this may take a moment.

```{r gh-installation, eval = FALSE}
# install.packages("devtools") 
devtools::install_github("KopfLab/tbltools")
```

## Functionality

### iRAT/tRAT Generation

The [tbltools](https://kopflab.github.io/tbltools/) package provides functionality to easily generate Readiness Assessment Tests from a collection of questions and answers (including images and equations) and any IF-AT answer key. For an example of how to use this functionality, see the vignette on [Generating a Readiness Assessment Test](https://kopflab.github.io/tbltools/articles/assessment_tests.html).

### Peer Evaluations

The [tbltools](https://kopflab.github.io/tbltools/) package also provides functionality to easily set up a peer evaluation server based on a student roster and team assignments and then evaluate the collected data. For an example of how to use this functionality, see the vignette on [Peer Evaluations](https://kopflab.github.io/tbltools/articles/peer_evaluations.html).

### Other functionality?

Ideas or suggestions for additional tools that would be helpful for running a flipped classroom? Let us know by filing a feature request at https://github.com/kopflab/tbltools/issues.
