---
title: "Readiness Assessment Test (RAT)"
date: "Date: `r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
  html_document:
    df_print: paged
  word_document: default
subtitle: "Module: ${module}"
geometry: margin=0.75in
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(tbltools)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
# Note: with echo = FALSE and message = FALSE as the default, code blocks do not show up on the final knitted document unless otherwise specified. 
# This means that code blocks can also be used to keep notes for onself when designing an iRAT/tRAT.
```

## Instructions

```{r}
# Note:
# You can write anything for the instructions. All markdown formatting will work.
# You can also use R code using the `r ...` syntax.
```

Fill out the iRAT score sheet by yourself. Once the time is up, return your iRAT score sheet and start the tRAT together with your team using the scratch-off sheets. Tally your team's tRAT with the following scoring guide: 4 points for one scratch, 2 points for 2 scratches, 1 point for 3 scratches and zero if you have to scratch four or more to reveal the correct answer.

## Questions

Choose the **best** answer among the alternatives. 

```{r, include = FALSE}
# Create RAT
RAT <-
  tbl_create_RAT_from_excel(
    "${excel_file}",
    filter_include = TRUE,
    fill_down_questions = TRUE
  ) %>% 
  tbl_arrange_RAT_questions(
    by = "original"
  )
RAT
```


```{r, results='asis'}
# Generate questions + answers
# Note: results = 'asis' is important to render the generated markdown
RAT %>% tbl_generate_RAT_choices(
  answer_layout = "vertical", # default layout
  answer_layout_column = "layout" # custom question layout
)
```


